Winter weather on exam dates and matriculation for a prestigious university in Japan

### 2021-04-07 Writeups/paper.tex
Revised up to 5. Results

\title{Winter weather on exam days and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The author would like to thank Laura Schechter for her numerous feedback and support. I am also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions. Any errors in this draft are the sole responsibility of the author.}}
\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The authors would like to thank Laura Schechter for her numerous feedback and support.}}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}

@@

This study analyzes the effect of winter weathers on exam outcomes in Japan.
Most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth), for admission.
Students take the exam on the same dates in mid-January in their prefectures.\footnote{
  There are 47 prefectures in Japan.
}
This creates a variation in weathers to which they are exposed on the exam dates.

@@

The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
The estimates are not only statistically but also economically significant.
Changing the temperature on the exam dates from 3-6 $^o$C to $<$ 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
Moreover, additional analyses suggest that the temperature in the morning on exam dates rather than the temperature during exams impact exam performance. 
The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.

This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
Several previous studies have found the adverse effect of high temperature on learning, which reduces performance at exams \citep{Park2020b, Cho2017}.
More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam days decreases the exam scores at high-stakes exams in China and the U.S., respectively.
Considering the importance of the effects the exam results can have on later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what we can do to ameliorate such effects.
To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.

This study also has a contribution to the literature on the economic impact of low temperature.
It has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}.
However, evidence based on data in the field is scarce.
Country-level studies have shown a non-linear effect of temperature on economic growth, in that both low and high temperature has a negative impact \citep{Burke2015}.
One study based on microdata is provided by \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
I use prefecture-level information to investigate how low temperature affects the cognitive performance of exam takers.

This study proceeds as follows.
In Section \ref{sec:background}, the context of this study is introduced.
Section \ref{sec:data} describes the data. 
Our empirical strategy is introduced in Section \ref{sec:empirical_strategy}.
In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.

@@

In Japan, for admission to public universities, students are usually required to take two exams.
The first-stage test is called Center Test.
Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
Most public universities, including UTokyo, require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
Questions are multiple-choice and common for all exam takers across Japan.
High-school seniors take the test at designated sites in the area where their high schools are located.
On the other hand, high-school graduates are assigned to test sites in the area where the homes used in their applications are located.\footnote{
  \citet{Watanabe2013} provides detailed descriptions on the administrations of Center Test.
}

Since January is the middle of winter in Japan, heavy snow can affect public transportation on exam dates.
This sometimes makes it difficult for exam takers to arrive at exam sites on time.
For the affected students, the following accommodations can be provided:
(i) delaying the start of exams by a few hours for all exam takers at a test site,
(ii) allowing them to take exams in a separate room, and
(iii) allowing them to take make-up exams a week later.
The same accommodations can be given to students who could not take exams for other reasons such as sickness or accidents in public transportation system.

@@

After Center Test, applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
UTokyo has the second-stage exam at the end of February for two days.\footnote{
  Up to 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
%  Most of the admissions were provided for exam takers in February:
%  In 2015, among 3,108 admitted students, only 100 exam takers in March got admitted.
  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admission process for those students. 
}

@@

I use two sets of data: weather and matriculation for UTokyo.
For weather information, I obtain data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
Based on hourly weather on exam days at prefecture capitals, I use average weather between 6 AM to 6 PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculate at UTokyo.
  %Moreover, it is unlikely that weathers on exam days affect decisions of admitted students to matriculate or not.
}

@@

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam days on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider a matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
}
%Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
%  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
%  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
%}
Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.

In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be the average temperature across two exam days in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam days as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam days, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam days.\footnote{
  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}$^,$\footnote{
  The figure shows that temperature is low for all prefectures in some years (eg. 2017) and is high in other years (eg. 2019).
  This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
  If this was the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
  Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
}

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam sites is measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.

%\begin{figure}[H]
%  \centering
%  \caption{Average temperature on two exam days in each prefecture each year}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
%  \label{fig:temperature_diff}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
%      Average across two test days in each year is shown in the figure.
%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
%  \end{tablenotes}
%\end{figure}

@@

In columns (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.13 percentage point.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather on exam days}
%  \input{"../Output/tex/main_reg.tex"}
%  \label{tab:main_reg}
%  \small
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

I further investigate if the findings above are due to weather in the morning or during the exams.
This distinction can be important since different measures should be taken to mitigate the effect of each weather.
The results are shown in Table \ref{tab:reg_morning_exam}.
Columns (1) and (2) show statistically significant impact of low temperature in the morning.
On the other hand, statistically insignificant estimates are obtained in columns (3) and (4) with weathers during the exams, although the magnitudes are large.
Also, including both kinds of weathers simultaneously, column (5) shows the negative and significant impact of cold weather in the morning on the matriculation share.\footnote{
  Estimates for cumulated snow are insignificant in column (5) due to multicollinearity, which blows up their standard errors.
  Their correlation coefficient is 0.99.
  This is reasonable since their differences can be caused by new snowfall or snow melting, which cannot happen drastically within hours.
}
This suggests that the morning weather on the exam dates matter for exam performance.

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
%  \scriptsize
%  \input{"../Output/tex/reg_morning_exam.tex"}
%  \label{tab:reg_morning_exam}
%  \scriptsize
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
%      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to  on exam days.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

One possible interpretation of the results is that the temperature on exam days captures the weather before the exam, which can affect preparation for the exam. 
For instance, cold weather can make it hard for students to focus on studying, or snowfalls can prevent students from going to schools or cram schools for studying.
To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for all the variables.
Therefore, I consider that the findings in Table \ref{tab:main_reg} are due to the effect of weather variables on the exam days.

@@

This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
%To identify the causal impact, I exploit the variation in weathers at each prefecture on exam days.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
This study fills the gap and identifies the causal impact of winter weather on matriculation.

The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam days.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.
Using the weather in the morning and during the exams, I find suggestive evidence that the temperature effect is mainly caused by low temperatures in the morning.
This result suggests that adverse conditions for exam takers on the way to test sites affect their cognitive performance.

Several implications can be derived from the findings.
First, the result that low temperature in the morning rather than during the exam matters suggests that investment to improve the condition at exam sites may have limited impacts.
Rather, for instance, it may be effective to provide sufficient time before the exam at exam sites so that students can recover in warm rooms.

Secondly, my results have implications for the admission process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
Also, they may change the weights for Center Test and the second-stage exam.
Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.

@@

\begin{figure}[H]
  \centering
  \caption{Average temperature on two exam days in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
  \label{fig:temperature_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

@@

\begin{table}[H]
  \center
  \caption{Regression: Matriculation share (\%) and weather on exam days}
  \input{"../Output/tex/main_reg.tex"}
  \label{tab:main_reg}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

\begin{table}[H]
  \center
  \caption{Regression: Matriculation share (\%) and weather in the morning vs. during exam}
  \scriptsize
  \input{"../Output/tex/reg_morning_exam.tex"}
  \label{tab:reg_morning_exam}
  \scriptsize
  \begin{tablenotes}
    \item
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      For variables in the morning, I use average weather variables at prefecture capitals between 6 AM to 9 AM on exam days.
      For variables during the exam, I use average weather variables at prefecture capitals between 9 AM to 6 PM on exam days.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}

>>>>

\title{Winter weather on exam dates and matriculation for a prestigious university in Japan}%: \\ Empirical analysis on auditing reports in Brazil}
%\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The author would like to thank Laura Schechter for her numerous feedback and support. I am also grateful to Joshua Deutschmann, Paul Dower, Jeremy Foltz, Priya Mukherjee, Andrew Stevens, and seminar participants at the UW-Madison Agricultural and Applied Economics department for helpful comments and suggestions. Any errors in this draft are the sole responsibility of the author.}}
\author{Mizuhiro Suzuki\thanks{Department of Agricultural and Applied Economics, University of Wisconsin-Madison. Contact: msuzuki7@wisc.edu. The authors would like to thank Laura Schechter for her numerous feedback and support.}}
\date{\today \\ \vspace{1cm} Preliminary draft \\ Please do not cite or circulate}

@@

This study analyzes the effect of winter weathers on exam outcomes in Japan.
For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
Students take the exam on the same dates in mid-January in their prefectures.\footnote{
  There are 47 prefectures in Japan.
}
This creates a variation in weathers to which they are exposed on the exam dates.

@@

The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
The estimates are not only statistically but also economically significant.
Changing the temperature on the exam dates from 3-6 $^o$C to lower than 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.

This study mainly contributes to the recent but growing literature of the effects of climate factors on the outcome of high-stakes exams.
Several previous studies have found the adverse effect of high temperature on learning, which reduces performance at exams \citep{Park2020b, Cho2017}.
More closely to my study, \citet{GraffZivin2020} and \citet{Park2020a} show that heat on exam dates decreases the exam scores at high-stakes exams in China and the U.S., respectively.
Considering the importance of the exam results for later life outcomes, it is important to understand how external factors such as temperature affect exam performance and what can be done to ameliorate such effects.
To complement the literature, I investigate the effect of \textit{low} temperature on exam performance.

This study also has a contribution to the literature on the economic impact of low temperature.
It has been shown with controlled experiments that cold stresses negatively affect such things as cognitive ability and memory, as reviewed in \citet{Taylor2016}.
However, evidence based on data in the field is scarce.
Country-level studies have shown a non-linear effect of temperature on economic growth, that is, both low and high temperature has a negative impact \citep{Burke2015}.
One study based on microdata is \citet{Stevens2017}, who finds a negative impact of low temperature on labor productivity of blueberry pickers in California.
I use prefecture-level information to investigate how low temperature affects the cognitive performance in a high-stakes exam.

This study proceeds as follows.
In Section \ref{sec:background}, the context of this study is introduced.
Section \ref{sec:data} describes the data. 
I introduced my empirical strategy in Section \ref{sec:empirical_strategy}.
In Section \ref{sec:results}, I present the empirical results, and Section \ref{sec:conclusion} concludes.

@@

In Japan, for admission to public universities, students are usually required to take two exams.
The first-stage test is called Center Test.
Students take an exam on consecutive two days (Saturday and Sunday) in mid-January.
Most public universities, including UTokyo, require students to take exams on social science, language, and English on the first day and math and natural science on the second day.
The exams start at 9:30 AM on both days and end at 6:10 PM on the first day and 5:50 PM on the second day.
Questions are multiple-choice and common for all exam takers across Japan.
High-school seniors take the test at designated sites in the exam area\footnote{ \label{footnote:prefecture}
  Typically, an exam area coincides with a prefecture (i.e. there is one exam area in one prefecture).
  Large prefectures such as Hokkaido and Okinawa have several exam areas.
  Also, several municipalities in a prefecture can be sometimes considered to be a part of a neighboring prefecture.
  For instance, students in a couple of municipalities in Saitama prefecture could take Center Test in Tokyo.
} where their high schools are located.
On the other hand, high-school graduates are assigned to test sites in the exam area where the homes used in their applications are located.\footnote{
  \citet{Watanabe2013} provides detailed descriptions on the administrations of Center Test.
}

Since January is the middle of winter in Japan, heavy snow can affect public transportation on exam dates.
This sometimes makes it difficult for exam takers to arrive at exam sites on time.
For the affected students, the following accommodations can be provided:
(i) delaying the start of exams by a few hours for all exam takers at a test site,
(ii) allowing the affected students to take exams in a separate room, and
(iii) allowing the affected students to take make-up exams a week later.
The same accommodations can be given to students who could not take exams for other reasons such as sickness or accidents.

@@

After Center Test, applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
UTokyo has the second-stage exam at the end of February for two days.\footnote{
  Until 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
%  Most of the admissions were provided for exam takers in February:
%  In 2015, among 3,108 admitted students, only 100 exam takers in March got admitted.
  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admission process for those students. 
}

@@

I use two sets of data: weather and matriculation for UTokyo.
For weather information, I obtain data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
Based on hourly weather on exam dates at prefecture capitals, I use average weather between 6 AM to 6 PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
  %Moreover, it is unlikely that weathers on exam dates affect decisions of admitted students to matriculate or not.
}

@@

The objective of the analysis is to analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider a matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students from the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
(ii) students from the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
}
%Secondly, since UTokyo is a national university, the tuition is cheaper than most private universities.\footnote{
%  According to \citet{mext}, in 2018, the annual tuition for national universities was 538,633 JPY ($\approx$ 4,900 USD), while the average annual tuition for private university was 904,146 ($\approx$ 8,200 USD).
%  %https://www.mext.go.jp/a_menu/koutou/shinkou/07021403/1412031_00001.htm
%}
Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse exam performance.

In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
I include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

I run the following regression equation:
\begin{equation*}
  Y_{jt} = f(T_{jt}) + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
\end{equation*}
I exploit the variation of temperature on exam dates, which I consider exogenous after controlling for prefecture-specific time-invariant factors and time-varying aggregate shocks through prefecture and year fixed effects.
As Figure \ref{fig:temperature_diff} shows, each prefecture experiences substantial variations in temperature on exam dates.\footnote{
  Figures for other weather variables are provided in Appendix \ref{sec:appendix_figure}.
}$^,$\footnote{
  The figure shows that temperature is low for most prefectures in some years (eg. 2017) and is high in other years (eg. 2019).
  This can bring up a concern that temperature \textit{deviations} from the prefecture average have limited variations within each year.
  If this was the case, most variations for estimation would be absorbed by prefecture fixed effects and year fixed effects.
  Figure \ref{fig:temperature_diff_by_year} shows that, even within each year, the temperature deviations have large variations across prefectures.
}

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam sites is measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
%\footnote{
%  In 2020, less than 40\% of the admitted students are high-school graduates.
%  In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
%  If I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$. 
%}
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.
Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
Since neighboring prefectures are geographically close, I consider that the effect of this measurement error on estimates is not large.

%\begin{figure}[H]
%  \centering
%  \caption{Average temperature on two exam dates in each prefecture each year}
%  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
%  \label{fig:temperature_diff}
%  \footnotesize
%  \begin{tablenotes}
%    \item Notes:
%      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
%      Average across two test days in each year is shown in the figure.
%      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
%  \end{tablenotes}
%\end{figure}

@@

In columns (3) and (4), I add other weather variables.
While temperature coefficients are barely affected, I find that rainfall and snowfall during exam time do not impact the matriculation shares.
On the other hand, the cumulated snow on the ground has a negative impact.
To capture the effect of the existence of a certain amount of snow on the ground, column (5) allows a non-linear effect of cumulated snow.
The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.13 percentage point.\footnote{
  Following the falsification test in \citet{Cho2017}, I check if weather variables one year after the actual Center Test affect the matriculation shares.
  The results in Table \ref{tab:reg_placebo_exam} show not only that the weather one year after Center Test has insignificant impacts on matriculation shares but also including the weather variables one year after Center Test barely change the coefficients on contemporaneous weather variables.
}

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and weather on exam dates}
%  \input{"../Output/tex/main_reg.tex"}
%  \label{tab:main_reg}
%  \small
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

One possible interpretation of the results is that the temperature on exam dates captures the weather before the exam due to the serial correlation.
In other words, the effects found in Table \ref{tab:main_reg} could be interpreted as the effects on preparation for the exam. 
For instance, cold weather can make it hard for students to focus on studying, suggested by existing studies \citep{Taylor2016}.
%Also, snowfall can prevent students from going to schools or cram schools for studying.
To investigate this possibility, I use the average weather variables for 10 days before the exams and run regressions.
The results in Table \ref{tab:reg_pre10} show statistically insignificant estimates for temperature variables.
This suggests that the negative impacts of low temperature found in Table \ref{tab:main_reg} are caused by the temperature on exam dates rather than temperature before exams.\footnote{
  Notice that the coefficients on snowfall and cumulated snow on the ground are statistically significant.
  Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
  (i) snow before the exams adversely can affect students' preparation, and
  (ii) snowfall before the exams cumulates snow on the grdound and students' performance is affected by the cumulated snow on the exam dates.
  Due to high collinearity of cumulated snow on the exam dates and 10 days before the exams, it is difficult to parse out these two mechanisms.
}

%\begin{table}[H]
%  \center
%  \caption{Regression: Matriculation share (\%) and average weather for 10 days before exam}
%  \input{"../Output/tex/reg_pre10.tex"}
%  \label{tab:reg_pre10}
%  \small
%  \begin{tablenotes}
%    \item
%      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
%      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
%      I use average weather variables at prefecture capitals between 10 days before and 1 day before the first day of Center Test.
%      Standard errors are clustered at the prefecture level.
%  \end{tablenotes}
%\end{table}

@@

This paper studies the impact of winter weather on cognitive performance on a high-stakes exam in Japan.
I use the matriculation share for the most prestigious university in Japan, the University of Tokyo.
%To identify the causal impact, I exploit the variation in weathers at each prefecture on exam dates.
Most of the existing studies in the literature have focused on the effect of heat on cognitive performance, while the impact of cold weather remains largely unknown.
This study fills the gap and identifies the causal impact of winter weather on matriculation.

The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.

The results have implications for the admission process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
Also, they may change the weights for Center Test and the second-stage exam.
Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes, it is desirable that universities take measures to mitigate the effect of nuisance factors on admission.

@@

\begin{figure}[H]
  \centering
  \caption{Average temperature on two exam dates in each prefecture each year}
  \includegraphics[width = 0.9\textwidth]{../Output/images/temperature_diff.pdf}
  \label{fig:temperature_diff}
  \footnotesize
  \begin{tablenotes}
    \item Notes:
      Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
      Average across two test days in each year is shown in the figure.
      Prefectures positioned to the left on the x-axis are located at more northern parts of Japan.
  \end{tablenotes}
\end{figure}

@@

\begin{table}[H]
  \center
  \caption{Regression: Matriculation share (\%) and weather on exam dates}
  \small
  \input{"../Output/tex/main_reg.tex"}
  \label{tab:main_reg}
  \small
  \begin{tablenotes}
    \item
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
      Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{table}
